### 2021-03-10 input/background.tex
wip

\begin{definition}[Fog infrastructure]
  A fog infrastructure is a connected \underline{g}raph $G(V, E)$ of
  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E \in
  V \times V$. Edges have symmetric \underline{w}eights $w_{ij} =
  w_{ji}$ with $i, j \in V$.
\end{definition}

Processes can send messages to their neighboring processes. Processes
can reliably broadcast messages by forwarding delivered
messages~\cite{nedelec2018causal,raynal2013distributed}. However,
reliable broadcast definition states that \emph{all} correct processes
should deliver broadcast messages. This proves costly in large scale
systems comprising thousands of processes. Instead, we define
\emph{scoped broadcast} where messages reach only interested
processes, significantly reducing generated traffic.

\begin{definition}[Scoped broadcast]
  \TODO{meow predicate, meow path, meow state, meow message.}
\end{definition}

This definition highlights the transitive relevance of sent messages
and encompasses more specific definitions of related
work~\cite{hsiao2005scoped,lue2006scoped,wang2015prodiluvian}.  A
process from Paris could scoped broadcast a message to all processes
in this city. A process from Paris could scoped broadcast a message to
all processes in this city plus neighboring cities by overloading
forwarded messages the first time they reach another city. As for
reliable broadcast, there exists different trade-off on space, time,
and communication.

\begin{definition}[Logical partition]
  A logical \underline{p}artition $P_s$ originated at a
  \underline{s}ource process $s \in V$ is a set of interconnected
  processes that do not belong to another logical partition. The set
  of sources is $S \subseteq V$.
\end{definition}

Processes belong to logical partitions depending on path weights. When
weights are about latency or hop numbers, the optimal partitioning
consists in processing the multiple destinations shortest path at each
process \REF.

\begin{definition}[Shortest path]
  A \underline{p}ath $\pi_{ij}$ from Process $i$ to Process $j$ is a
  sequence of vertices $[i, k_1, k_2, \ldots k_n, j]$ with $\forall
  0\leq m \leq n, \langle \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in
  E$. Shortest \underline{p}aths $\Pi_{ij}$ are sets of paths such
  that there exists no lower sum of weights $|\Pi_{ij}|$ from $i$ to
  $j$.
\end{definition}

\begin{definition}[Optimal partitioning]
  The optimal partitioning $\mathcal{P}$ is a set of logical
  partitions such that each process belongs to a logical partition
  comprising its closest source process.  $\forall p \in P_{s_1\in S},
  \nexists P_{s_2 \in S}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
\end{definition}

Processes use reliable asynchronous message passing to reach optimal
partitioning together. Process $s$ generates a message
$\alpha_s^0$. Upon \underline{r}eceipt $r_i(\alpha_s^{w})$, Process
$i$ knows that Process $s$ created a partition at a path length of
$w$. Process $i$ may choose to \underline{d}eliver $d_i(\alpha_s^{w})$
if it improves its partitioning. Process $i$ may choose to propagate
its change through \underline{b}roadcast $b_i(\alpha_s^w)$.  Without
global knowledge, processes only rely on their own behavior to deduce
the behavior of their neighbor processes.

@@

\begin{definition}[\label{def:transitivedelivery}Transitive delivery]
  Transitive delivery ensures the system eventually converges to
  optimal partitioning:
  \begin{inparaenum}[(i)]
  \item (\textbf{termination}) processes do not need to propagate
    operations they do not deliver: $\forall \langle i, j \rangle \in
    E, \neg d_i(\alpha_{s}^w)\implies \neg
    d_j(\alpha_{s}^{w+w_{ij}})$;
  \item (\textbf{propagation}) operations delivered by a process may
    also benefit neighbor processes: $\forall \langle i, j \rangle \in
    E, d_i(\alpha_{s}^{w_1}) \implies
    d_j(\alpha_{s}^{w_1+w_{ij}}) \vee
    d_j(\alpha_{*}^{w_2 < w_1 + w_{ij}})$.
  \end{inparaenum}
\end{definition}

@@

Algorithm~\ref{algo:add} shows the instructions that implement the
rules of Definition~\ref{def:transitivedelivery} to converge towards
optimal partitioning. Figure~\ref{fig:add} illustrates its behavior on
a system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
$a$ and $c$ concurrently create a partition. They initialize their own
state with the lowest possible bound $0$ (see
Line~\ref{line:lowestbound}), and send a message to each of their
neighbors by accumulating the corresponding edge weight (see
Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process $b$
receives $\alpha_{c}^{1}$. Since it improves its own partition
distance, it keeps it and forwards it to its neighbors. Process $b$
discards $\alpha_{b}^{1.5}$, for it does not improve its partition
distance. Processes $c$ and $d$ will never hear of Process $a$'s
partition. At scale, such \emph{scoped flooding} saves bandwidth by
limiting generated traffic to subsets of
processes~\cite{wang2015prodiluvian}. In Figure~\ref{fig:addD},
processes discard last transiting messages. The system converged to
the optimal partitioning.  Transitive relationships ensure that each
process gets its closest source while accumulation of weights ensures
that messages propagation terminates.  Interestingly, while the
receipt order of messages does not impact on local control information
($r_b(\alpha_a^{1.5}) \cdot r_b(\alpha_a^{1}) \Leftrightarrow
r_b(\alpha_a^{1}) \cdot r_b(\alpha_a^{1.5}) \implies
\TODO{d_b(\alpha_a^{1})}$), it impacts on control information
broadcast in the network ($r_b(\alpha_a^{1.5}) \cdot r_b(\alpha_a^{1})
\implies b_b(\alpha_{b}^{1.5}) \cdot b_b(\alpha_{b}^{1})$ while
$r_b(\alpha_a^{1}) \cdot r_b(\alpha_a^{1.5}) \implies
b_b(\alpha_a^{1})$).

>>>>

\begin{definition}[Fog infrastructure]
  A fog infrastructure is a connected \underline{g}raph $G(V, E)$ of
  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
  \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from Process
  $i$ to Process $j$ is a sequence of vertices $[i, k_1, k_2, \ldots
    k_n, j]$ with $\forall m: 0\leq m \leq n, \langle \pi_{ij}[m],
  \pi_{ij}[m+1] \rangle \in E$.
\end{definition}

Processes can send messages to their neighboring processes. Processes
can reliably broadcast messages by forwarding delivered
messages~\cite{hadzilacos1994modular,nedelec2018causal,raynal2013distributed}. However,
uniform reliable broadcast states that \emph{all} correct processes
must deliver broadcast messages. This proves costly in large scale
systems comprising thousands of processes. Instead, we define
\emph{scoped broadcast} where messages reach only interested
processes, significantly reducing generated traffic.

\begin{definition}[\underline{S}coped broadcast (S-broadcast)]
  When Process $x$ scoped \underline{b}roadcasts $b_x(m)$ a
  \underline{m}essage $m$, every correct Process $y$ within a scope
  \underline{r}eceives $r_y(m)$ and \underline{d}elivers it
  $d_y(m)$. The scope depends on \underline{s}tates $\sigma$ of
  processes, \underline{m}etadata $\mu$ within received messages, and
  a \underline{p}redicate $\phi$ verified from process to process:
  $b_x(m) \wedge r_y(m) \implies \exists \pi_{xy} : \forall z \in
  \pi_{xy}, \phi(\mu_z, \sigma_z)$.
\end{definition}

This definition highlights the transitive relevance of messages and
encompasses more specific definitions of related
work~\cite{hsiao2005scoped,lue2006scoped,wang2015prodiluvian}.  A
process from Paris could scoped broadcast a message to all processes
in this city. A process from Paris could scoped broadcast a message to
all processes in this city plus neighboring cities by overloading
forwarded messages the first time they reach another city. Similarly
to reliable broadcast, scoped broadcast implementations expose
different trade-offs on space, time, and communication.

%% \begin{definition}[S-broadcast properties]
%%   S-broadcast guarantees 3 properties:
%%   \begin{inparaenum}[(i)]
%%   \item Validity: If a correct process broadcasts a message, it
%%     eventually delivers it;
%%   \item Scoped Agreement: If a process broadcasts a message, then all
%%     correct processes within the scope eventually delivers it;
%%   \item Scoped Integrity: A process delivers a message only if it was
%%     previously broadcast within the scope.
%%   \end{inparaenum}
%% \end{definition}

In this paper, we propose to dynamically adapt the scope of
S-broadcast using S-broadcast itself.  \textbf{First}, at any time, a
process can become the source of a new logical partition by
transitively modifying the respective state of neighboring processes
using path weights.  When a process S-broadcasts a message in this
partition, it reaches all processes belonging to this partition. While
the first partition gathers all processes of the system, the following
partitions reduce the membership size of their neighboring
partitions. In turns, the traffic generated to adapt scopes scales
with the number of partitions.

\begin{definition}[Consistent partitioning]
  Let $S \subseteq V$ be the set of \underline{s}ources, $W_{xy} =
  W_{yx}$ be the symetric \underline{w}eight between $x$ and $y$,
  $\Pi_{xz}$ be the shortest \underline{p}ath from $x$ to $z$ the
  weight of which $|\Pi_{xz}|$ is lower than any other path weight,
  the consistent partitioning $\mathcal{P}$ is a set of logical
  partitions $P_{s\in S}$ such that each process belongs to a logical
  partition comprising its closest source process.  $\forall p \in
  P_{s_1}, \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
\end{definition}

@@

%% \begin{definition}[\label{def:transitivedelivery}Transitive delivery]
%%   Transitive delivery ensures the system eventually converges to
%%   optimal partitioning:
%%   \begin{inparaenum}[(i)]
%%   \item (\textbf{termination}) processes do not need to propagate
%%     operations they do not deliver: $\forall \langle i, j \rangle \in
%%     E, \neg d_i(\alpha_{s}^w)\implies \neg
%%     d_j(\alpha_{s}^{w+w_{ij}})$;
%%   \item (\textbf{propagation}) operations delivered by a process may
%%     also benefit neighbor processes: $\forall \langle i, j \rangle \in
%%     E, d_i(\alpha_{s}^{w_1}) \implies
%%     d_j(\alpha_{s}^{w_1+w_{ij}}) \vee
%%     d_j(\alpha_{*}^{w_2 < w_1 + w_{ij}})$.
%%   \end{inparaenum}
%% \end{definition}

@@

Algorithm~\ref{algo:add} shows the instructions that implement
eventually consistent partitioning when weights are scalar values.

%% Processes use reliable asynchronous message passing to reach optimal
%% partitioning together. When Process $s$ wants to become a source, it
%% generates a message $\alpha_s^0$. Upon \underline{r}eceipt
%% $r_i(\alpha_s^{w})$, Process $i$ knows that Process $s$ created a
%% partition at a path length of $w$. Process $i$ may choose to
%% \underline{d}eliver $d_i(\alpha_s^{w})$ if it improves its
%% partitioning. Process $i$ may choose to propagate its change through
%% \underline{b}roadcast $b_i(\alpha_s^w)$.  Without global knowledge,
%% processes only rely on their own behavior to deduce the behavior of
%% their neighbor processes.

\TODO{the rules of Definition~\ref{def:transitivedelivery} to converge
towards optimal partitioning. Figure~\ref{fig:add} illustrates its
behavior on a system comprising 4 processes $a$, $b$, $c$, and
$d$. Two processes $a$ and $c$ concurrently create a partition. They
initialize their own state with the lowest possible bound $0$ (see
Line~\ref{line:lowestbound}), and send a message to each of their}
neighbors by accumulating the corresponding edge weight (see
Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process $b$
receives $\alpha_{c}^{1}$. Since it improves its own partition
distance, it keeps it and forwards it to its neighbors. Process $b$
discards $\alpha_{b}^{1.5}$, for it does not improve its partition
distance. Processes $c$ and $d$ will never hear of Process $a$'s
partition. At scale, such \emph{scoped flooding} saves bandwidth by
limiting generated traffic to subsets of
processes~\cite{wang2015prodiluvian}. In Figure~\ref{fig:addD},
processes discard last transiting messages. The system converged to
the optimal partitioning.  Transitive relationships ensure that each
process gets its closest source while accumulation of weights ensures
that messages propagation terminates.  Interestingly, while the
receipt order of messages does not impact on local control information
($r_b(\alpha_a^{1.5}) \cdot r_b(\alpha_a^{1}) \Leftrightarrow
r_b(\alpha_a^{1}) \cdot r_b(\alpha_a^{1.5}) \implies
\TODO{d_b(\alpha_a^{1})}$), it impacts on control information
broadcast in the network ($r_b(\alpha_a^{1.5}) \cdot r_b(\alpha_a^{1})
\implies b_b(\alpha_{b}^{1.5}) \cdot b_b(\alpha_{b}^{1})$ while
$r_b(\alpha_a^{1}) \cdot r_b(\alpha_a^{1.5}) \implies
b_b(\alpha_a^{1})$).
